---
title: "LOVER OF WISDOM"
author: "Jessie Yu (UNI:jy3161)"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{css header-colors, echo = FALSE}
.page-header {
    background-image: linear-gradient(90deg,#be93c5,#7bc6cc)
}
```

```{r setup, include = FALSE, eval = TRUE}
knitr::opts_chunk$set(eval = TRUE, echo = FALSE, warning = FALSE)
```

## 0. Install and Load Libraries
```{r}
packages.used=c("tm", "wordcloud", "RColorBrewer", 
                "dplyr", "tidytext", "stringr", "ggplot2", "sentimentr", "ggpubr")
# check packages that need to be installed.
packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))
# install additional packages
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE,
                   repos='http://cran.us.r-project.org')
}
```

```{r, echo = TRUE, message = FALSE}
library(tm)
library(wordcloud)
library(RColorBrewer)
library(dplyr)
library(tidytext)
library(stringr)
library(ggplot2)
library(sentimentr)
library(ggpubr)
```

This notebook was prepared with the following environmental settings.
```{r}
print(R.version)
```


## 1.About the data

The dataset for this project can be found at [Philosophy dataset](https://www.kaggle.com/kouroshalizadeh/history-of-philosophy). 
"The dataset contains over 300,000 sentences from over 50 texts spanning 10 major schools of philosophy. The represented schools are: Plato, Aristotle, Rationalism, Empiricism, German Idealism, Communism, Capitalism, Phenomenology, Continental Philosophy, and Analytic Philosophy.The texts were cleaned extensively before being tokenized and organized in the way they're presented here."


Hang on to the interesting discoveries for a second! Let's first take a look at the dataset! 
```{r read dataset, include = FALSE}
philosophy <- readr::read_csv("/Users/apple/Desktop/5243ADS/spring-2022-prj1-JessieYu3161/data/philosophy_data.csv")
```


```{r, echo = TRUE}
head(philosophy)
```
Checking for NAs: 
```{r echo = TRUE}
sum(is.na(philosophy) == "TRUE")
```
- Great! There is no NAs in our dataset. (not surprising, since the dataset is pre-processed as mentioned above)



Now, let's get a sense of the length of sentences said by philosophers in each School. Here, I used the pre-processed and pre-defined value in the original dataset, the tokenized texts, and create a new variable that corresponding to the length of the sentences, number of words. 
```{r echo = TRUE}
# add new column: number of tokens 
philosophy$`n_tokens` <- str_count(philosophy$tokenized_txt, "\\w+")
```

Using data visualization to discover the length of sentences by School:
```{r echo = TRUE}
ggplot(data = philosophy, aes(x = school, y = n_tokens)) +
  geom_boxplot(color="dodgerblue", fill="blue", alpha=0.1, notch=TRUE, notchwidth = 0.9) +
  theme(axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
  ggtitle("Length of Sentences") + xlab("School") + ylab("Number of Tokens")
```

From the data frame below, which grouped by School, Author, and Title, the last column represents the number of works of its corresponding divisions. 

```{r echo = TRUE}
as.data.frame(philosophy %>%
    group_by(school,author,title) %>%
    count(title)) %>%
    arrange(desc(n))
```
## 2. The Word Clouds 'Collection'

Let's dig in more!! 

I explored the data by unnesting the tokenized text and removing the less meaningful words, removing the stopwords in English, and generated word frequency tables.

<p style="text-align: center;">**Which words were most frequently used by these philosophers ?**</p>

<p style="text-align: center;">Check out this *Overall Wordcloud* !</p>
```{r, fig.align = 'center', echo = TRUE}
overall.words <- philosophy %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 

wordcloud(overall.words$words, overall.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))
```


It is worth noticing after removing the stopwords, the most frequently used words by the philosophers is 'ONE', and also other words "can", "will", "must"...

Now, let us get a closer look and focus on each School!

Word clouds by School(ordered by the amount of sentences from high to low):

Notice: here I only present one chunk of code to demonstrate the coding for first three school's word cloud, more details can be found on my [Github Page](https://github.com/TZstatsADS/spring-2022-prj1-JessieYu3161). 


```{r fig.align = 'center', echo = TRUE}
par(mfrow= c(1,3), mar = c(1,1,1,1))

analytic.words <- philosophy %>%
  filter(school == "analytic") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


analytic.wc <- wordcloud(analytic.words$words, analytic.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))

aristotle.words <- philosophy %>%
  filter(school == "aristotle") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


aristotle.wc <- wordcloud(aristotle.words$words, aristotle.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))

plato.words <- philosophy %>%
  filter(school == "plato") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(plato.words$words, plato.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))
```

<center>Analytic, Aristotle , and Plato Word Clouds</center>



```{r fig.align = 'center'}
par(mfrow= c(1,3), mar = c(1,1,1,1))

german_idealism.words <- philosophy %>%
  filter(school == "german_idealism") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(german_idealism.words$words, german_idealism.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))


continental.words <- philosophy %>%
  filter(school == "continental") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(continental.words$words, continental.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))

phenomenology.words <- philosophy %>%
  filter(school == "phenomenology") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(phenomenology.words$words, phenomenology.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))
```

<center>German Idealism, Continental, and Phenomenology Word Cloud</center>



```{r fig.align = 'center'}
par(mfrow= c(1,3), mar = c(1,1,1,1))
rationalism.words <- philosophy %>%
  filter(school == "rationalism") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(rationalism.words$words, rationalism.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))

empiricism.words <- philosophy %>%
  filter(school == "empiricism") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(empiricism.words$words, empiricism.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))

feminism.words <- philosophy %>%
  filter(school == "feminism") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(feminism.words$words, feminism.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))
```


<center>Rationalism, Empiricism, and Feminism Word Cloud</center>


```{r fig.align = 'center'}
par(mfrow= c(1,3), mar = c(1,1,1,1))


capitalism.words <- philosophy %>%
  filter(school == "capitalism") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(capitalism.words$words, capitalism.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))

communism.words <- philosophy %>%
  filter(school == "communism") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(communism.words$words, communism.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))

nietzsche.words <- philosophy %>%
  filter(school == "nietzsche") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(nietzsche.words$words, nietzsche.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))
```

<center>Capitalism, Communism, and Nietzsche Word Cloud</center>

```{r fig.align = 'center'}
stoicism.words <- philosophy %>%
  filter(school == "stoicism") %>% 
  select(tokenized_txt) %>% 
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  count(words, sort = TRUE) 


wordcloud(stoicism.words$words, stoicism.words$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))
```

<center>Stoicism Word Cloud</center>

It is interesting to see Rationalism most frequently used word is "GOD", "the rationalists discovered God through the natural world, but in a different way. Rationalists thought it unlikely that God would choose to reveal himself only at particular times to particular people." If you take a look at the Feminism, Capitalism, and Communism Word Cloud, these are rather intuitional and congenital. 


## 3. Sentiment Analysis 

For sentiment analysis in this section, I'm using NRC Word-Emotion Association Lexicon, *more details can be found here* [NRC_Lexicon](http://saifmohammad.com/WebPages/NRC-Emotion-Lexicon.htm). 

Let's first look at Plato, Aristotle, and Nietzsche, who are the only author corresponding to each school in our dataset!
```{r}
philosophy %>%
  filter(school == "plato" | school == "aristotle" | school == "nietzsche") %>%
  select(author) %>%
  distinct(author)
```


Here, I calculated the frequency of each sentimental words used by each author and assign colors by sentiment type. Notice that I filtered out "positive" and "negative" categories in the sentiment types, we focus on emotions here (anger, anticipation, disgust, fear, joy, sadness, surprise, and trust). 

```{r, echo = TRUE, include = TRUE, message = FALSE}
plato.sentiment <- plato.words %>%
  rename(word = words) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment) %>%
  summarise(sentiment_freq =sum(n))

plato.s.p <- plato.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(sentiment, sentiment_freq, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
  xlab("Sentiment") + ylab("Frequency")
```


```{r, echo = TRUE, include = TRUE, message = FALSE, message = FALSE}
aristotle.sentiment <- aristotle.words %>%
  rename(word = words) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment) %>%
  summarise(sentiment_freq =sum(n))

aristotle.s.p <- aristotle.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(sentiment, sentiment_freq, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
 xlab("Sentiment") + ylab("Frequency")
```

```{r, echo = TRUE, include = TRUE, message = FALSE}
nietzsche.sentiment <- nietzsche.words %>%
  rename(word = words) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment) %>%
  summarise(sentiment_freq =sum(n))

nietzsche.s.p <- nietzsche.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(sentiment, sentiment_freq, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
  xlab("Sentiment") + ylab("Frequency")
```

```{r, out.width="90%", echo = TRUE, include = TRUE}
s.p <- ggarrange(plato.s.p, aristotle.s.p, nietzsche.s.p, ncol = 3, nrow = 1, common.legend = TRUE)
annotate_figure(s.p, top = text_grob("Plato  vs.  Aristotle  vs.  Nietzsche Sentiment Analysis by Author"))
```


As for the rest of the school, each school has multiple number of authors. Let's compare them! For a more intuitive and informative perception, I calculated the percentage of each sentimental words used by each author. Colors are assigned based on sentiment types. 

Notice: The coding for each school is repetitive and here I would only show Analytic school for demonstration, for more details [Github Page](https://github.com/TZstatsADS/spring-2022-prj1-JessieYu3161). 

```{r, echo = TRUE, include = TRUE, message = FALSE}
analytic.sentiment <- philosophy %>%
  filter(school == "analytic") %>% 
  select(author,tokenized_txt) %>%
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  rename(word = words) %>%
  group_by(author) %>%
  mutate(n_words = n()) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment, author, n_words) %>%
  summarise(sentiment_freq = n()) %>%
  mutate(percentage = round(sentiment_freq/n_words*100, 1))

analytic.s.p <- analytic.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(author, percentage, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  scale_fill_brewer(palette="Pastel1") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
   ggtitle("Analytic Sentiment Analysis") + xlab("Authors") + ylab("Percentage")
```



```{r, message = FALSE}
feminism.sentiment <- philosophy %>%
  filter(school == "feminism") %>% 
  select(author,tokenized_txt) %>%
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  rename(word = words) %>%
  group_by(author) %>%
  mutate(n_words = n()) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment, author, n_words) %>%
  summarise(sentiment_freq = n()) %>%
  mutate(percentage = round(sentiment_freq/n_words*100, 1))

feminism.s.p <- feminism.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(author, percentage, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  scale_fill_brewer(palette="Pastel1") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
   ggtitle("Feminism Sentiment Analysis") + xlab("Authors") + ylab("Percentage")

```

```{r, out.width="90%", echo = TRUE, include = TRUE}
ggarrange(analytic.s.p, feminism.s.p, ncol = 2, nrow = 1, common.legend = TRUE)
```


```{r, message = FALSE}
capitalism.sentiment <- philosophy %>%
  filter(school == "capitalism") %>% 
  select(author,tokenized_txt) %>%
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  rename(word = words) %>%
  group_by(author) %>%
  mutate(n_words = n()) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment, author, n_words) %>%
  summarise(sentiment_freq = n()) %>%
  mutate(percentage = round(sentiment_freq/n_words*100, 1))

capitalism.s.p <- capitalism.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(author, percentage, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  scale_fill_brewer(palette="Pastel1") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
   ggtitle("Capitalism Sentiment Analysis") + xlab("Authors") + ylab("Percentage")
```

```{r, message = FALSE}
stoicism.sentiment <- philosophy %>%
  filter(school == "stoicism") %>% 
  select(author,tokenized_txt) %>%
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  rename(word = words) %>%
  group_by(author) %>%
  mutate(n_words = n()) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment, author, n_words) %>%
  summarise(sentiment_freq = n()) %>%
  mutate(percentage = round(sentiment_freq/n_words*100, 1))

stoicism.s.p <- stoicism.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(author, percentage, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  scale_fill_brewer(palette="Pastel1") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
   ggtitle("Stoicism Sentiment Analysis") + xlab("Authors") + ylab("Percentage")
```

```{r, message = FALSE}
empiricism.sentiment <- philosophy %>%
  filter(school == "empiricism") %>% 
  select(author,tokenized_txt) %>%
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  rename(word = words) %>%
  group_by(author) %>%
  mutate(n_words = n()) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment, author, n_words) %>%
  summarise(sentiment_freq = n()) %>%
  mutate(percentage = round(sentiment_freq/n_words*100, 1))

empiricism.s.p <- empiricism.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(author, percentage, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  scale_fill_brewer(palette="Pastel1") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
   ggtitle("Empiricism Sentiment Analysis") + xlab("Authors") + ylab("Percentage")
```


```{r, message = FALSE}
rationalism.sentiment <- philosophy %>%
  filter(school == "rationalism") %>% 
  select(author,tokenized_txt) %>%
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  rename(word = words) %>%
  group_by(author) %>%
  mutate(n_words = n()) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment, author, n_words) %>%
  summarise(sentiment_freq = n()) %>%
  mutate(percentage = round(sentiment_freq/n_words*100, 1))

rationalism.s.p <- rationalism.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(author, percentage, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  scale_fill_brewer(palette="Pastel1") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
   ggtitle("Rationalism Sentiment Analysis") + xlab("Authors") + ylab("Percentage")
```

```{r, message = FALSE}
continental.sentiment <- philosophy %>%
  filter(school == "continental") %>% 
  select(author,tokenized_txt) %>%
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  rename(word = words) %>%
  group_by(author) %>%
  mutate(n_words = n()) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment, author, n_words) %>%
  summarise(sentiment_freq = n()) %>%
  mutate(percentage = round(sentiment_freq/n_words*100, 1))

continental.s.p <-continental.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(author, percentage, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  scale_fill_brewer(palette="Pastel1") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
   ggtitle("Continental Sentiment Analysis") + xlab("Authors") + ylab("Percentage")
```

```{r, message = FALSE}
phenomenology.sentiment <- philosophy %>%
  filter(school == "phenomenology") %>% 
  select(author,tokenized_txt) %>%
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  rename(word = words) %>%
  group_by(author) %>%
  mutate(n_words = n()) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment, author, n_words) %>%
  summarise(sentiment_freq = n()) %>%
  mutate(percentage = round(sentiment_freq/n_words*100, 1))

phenomenology.s.p <- phenomenology.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(author, percentage, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  scale_fill_brewer(palette="Pastel1") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
   ggtitle("Phenomenology Sentiment Analysis") + xlab("Authors") + ylab("Percentage")
```

```{r, message = FALSE}
german_idealism.sentiment <- philosophy %>%
  filter(school == "german_idealism") %>% 
  select(author,tokenized_txt) %>%
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  rename(word = words) %>%
  group_by(author) %>%
  mutate(n_words = n()) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment, author, n_words) %>%
  summarise(sentiment_freq = n()) %>%
  mutate(percentage = round(sentiment_freq/n_words*100, 1))

german_idealism.s.p <- german_idealism.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(author, percentage, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  scale_fill_brewer(palette="Pastel1") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
   ggtitle("German_Idealism Sentiment Analysis") + xlab("Authors") + ylab("Percentage")
```

```{r, message = FALSE}
communism.sentiment <- philosophy %>%
  filter(school == "communism") %>% 
  select(author,tokenized_txt) %>%
  unnest_tokens(words, tokenized_txt, token = "words") %>%
  filter(!(words %in% stopwords("English"))) %>%
  rename(word = words) %>%
  group_by(author) %>%
  mutate(n_words = n()) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F) %>%
  group_by(sentiment, author, n_words) %>%
  summarise(sentiment_freq = n()) %>%
  mutate(percentage = round(sentiment_freq/n_words*100, 1))

communism.s.p <- communism.sentiment %>% filter(sentiment != "positive", sentiment != "negative") %>%
  ggplot(aes(author, percentage, fill = sentiment)) +    
  geom_bar(stat="identity",   
           position=position_dodge()) + 
  scale_fill_brewer(palette="Pastel1") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(color = "rosybrown", 
                           size = 9, angle = 45),
          axis.text.y = element_text(color = "rosybrown", 
                           size = 9, angle = 45), 
        plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "aliceblue")) +
   ggtitle("Communism Sentiment Analysis") + xlab("Authors") + ylab("Percentage")
```


```{r out.width="90%"}
ggarrange(capitalism.s.p, stoicism.s.p, ncol = 2, nrow = 1, common.legend = TRUE)
```

```{r out.width="90%"}
ggarrange(empiricism.s.p, rationalism.s.p, ncol = 2, nrow = 1, common.legend = TRUE)
```

```{r out.width="90%"}
ggarrange(continental.s.p, phenomenology.s.p, ncol = 2, nrow = 1, common.legend = TRUE)
```

```{r out.width="90%"}
ggarrange(german_idealism.s.p, communism.s.p, ncol = 2, nrow = 1, common.legend = TRUE)
```

As the above visualizations present, "trust" words are indeed popular!!! "Trust" words are defined as "Positive" sentiment and they are a big deal to philosophers. 

<center>Curious about what "trust" words are used? </center>
```{r, include = TRUE, echo = TRUE}
trust <- overall.words %>%
  rename(word = words) %>%
  left_join(get_sentiments("nrc"), by = "word") %>%
  mutate(sentiment = factor(sentiment)) %>%
  filter(is.na(sentiment) == F, sentiment == "trust")

wordcloud(trust$word, trust$n,
          scale=c(3,0.35),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.25,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Pastel1"))
```




